---
title: "CS 101 (Data Preparation) Practical Exam"
author: "Jonash Lor Defensor"
date: "2024-03-07"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
A. Load the built-in warpbreaks dataset.

#1. Find out, in a single command, which columns of warpbreaks are either numeric or integer. What are the data types of each column?

```{r}
numeric_columns <- sapply(warpbreaks, function(x) is.numeric(x) || is.integer(x))
print(numeric_columns)
```
# 2. How many observations does it have?
```{r}
warpbreaks[, numeric_columns] <- sapply(warpbreaks[, numeric_columns], as.integer)
print(warpbreaks)
```
# 3. Is numeric a natural data type for the columns which are stored as such? Convert to integer when necessary.
Answer: Yes
```{r}
numeric <- as.integer(warpbreaks$breaks)
```
# 4. Error in 1:ncol(numeric_or_integer_columns) : argument of length 0

B. Load the exampleFile.txt
# 1. Read the complete file using readLines.
```{r}
file_path <- "/cloud/project/LabExercise1/exampleFile.txt"
lines <- readLines(file_path, warn = FALSE)
print(lines)
```
# 2. Separate the vector of lines into a vector containing comments and a vector containing the data. Hint: use grepl.
```{r}
comments <- lines[grepl("^#", lines)]
print(comments)
data_lines <- lines[!grepl("^#", lines)]
print(data_lines)
```
# 3. Extract the date from the first comment line and display on the screen “It was created data.”
```{r}
date_line <- comments[1]
print(date_line)
date <- gsub("# Date: ", "", date_line)
print(date)
```
# 4. Read the data into a matrix as follows.
# a. Split the character vectors in the vector containing data lines by semicolon (;) using strsplit.
```{r}
split_data <- strsplit(data_lines, ";")
print(split_data)
```
# b. Find the maximum number of fields retrieved by split. Append rows that are shorter with NA's.
```{r}
max_fields <- max(sapply(split_data, length))
print(max_fields)
split_data <- lapply(split_data, function(x) {
  if (length(x) < max_fields) {
    c(x, rep(NA, max_fields - length(x)))
  } else {
    x
  }
})
print(split_data)
```
# c. Use unlist and matrix to transform the data to row-column format.
```{r}
data_matrix <- matrix(unlist(split_data), nrow = length(split_data), byrow = TRUE)
print(data_matrix)
```
# d. From comment lines 2-4, extract the names of the fields. Set these as colnames for the matrix you just created.
```{r}
field_names <- gsub("# ", "", comments[2:4])
print(field_names)
dim(data_matrix)

field_names <- strsplit(field_names, ": ")[[1]]
print(field_names)
length_field_names <- length(field_names)
print(length_field_names)

if (ncol(data_matrix) != length_field_names) {
  # Handle the mismatch (adjust your code accordingly)
  print("Number of columns and length of column labels do not match.")
} else {
  colnames(data_matrix) <- field_names
}
