---
title: "lab_exercise#1_defensor"
author: "Jonash Lor Defensor"
date: "2024-02-10"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Scraping for Pencils

```{r}

#install.packages("dplyr")
#install.packages("rvest")
#install.packages("polite")
#install.packages("httr")

library(dplyr)
library(rvest)
library(polite)
library(httr)
```

```{r}
pencil_products <- data.frame()
```

```{r}
pencillink1 = "https://www.amazon.co.uk/s?k=pencil&crid=12INRWS90A0P1&sprefix=pencil%2Caps%2C659&ref=nb_sb_noss_1"

session1 <- bow(pencillink1,
           user_agent = "For Educational Purpose")
```

```{r}
scrapeNodes <- function(selector){
scrape(session) %>%
  html_nodes(selector) %>%
  html_text(trim = TRUE)
}
```

```{r}
scrapedCategory <- "Pencil"
```

```{r}
scrapedName <- scrapeNodes("h2.a-size-mini.a-spacing-none.a-color-base.s-line-clamp-4")
scrapedName <- scrapedName[1:45]

scrapedPrice <- scrapeNodes("span.a-offscreen")
scrapedPrice <- scrapedPrice[1:45]

scrapedRatings <- scrapeNodes("span.a-icon-alt")
scrapedRatings <- scrapedRatings[1:45]

scrapedReviews <- scrapeNodes("span.a-size-base.s-underline-text")
scrapedReviews <- scrapedReviews[1:45]
```

```{r}
pencil_products <- rbind(pencil_products, data.frame(category = scrapedCategory,name = scrapedName,
                    price = scrapedPrice,
                    ratings = scrapedRatings,
                    no_of_reviews = scrapedReviews))
```
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
```{r}

pencillink2 = "https://www.amazon.co.uk/s?k=pencil&page=2&crid=12INRWS90A0P1&qid=1707581214&sprefix=pencil%2Caps%2C659&ref=sr_pg_2"
```
```{r}

session2 <- bow(pencillink2,
           user_agent = "For Educational Purpose")
```
```{r}
scrapedCategory2 <- "Pencil"
```
```{r}
scrapedName2 <- scrapeNodes("h2.a-size-mini.a-spacing-none.a-color-base.s-line-clamp-4")
scrapedName2 <- scrapedName2[1:45]

scrapedPrice2 <- scrapeNodes("span.a-offscreen")
scrapedPrice2 <- scrapedPrice2[1:45]

scrapedRatings2 <- scrapeNodes("span.a-icon-alt")
scrapedRatings2 <- scrapedRatings2[1:45]

scrapedReviews2 <- scrapeNodes("span.a-size-base.s-underline-text")
scrapedReviews2 <- scrapedReviews2[1:45]
```
```{r}

pencil_products <- rbind(pencil_products, data.frame(category = scrapedCategory,name = scrapedName,
                    price = scrapedPrice,
                    ratings = scrapedRatings,
                    no_of_reviews = scrapedReviews))

```
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
```{r}
pencillink3 = "https://www.amazon.co.uk/s?k=pencil&page=3&crid=12INRWS90A0P1&qid=1707584881&sprefix=pencil%2Caps%2C659&ref=sr_pg_3"

session3 <- bow(pencillink3,
           user_agent = "For Educational Purpose")

scrapedCategory3 <- "Pencil"

scrapedName3 <- scrapeNodes("h2.a-size-mini.a-spacing-none.a-color-base.s-line-clamp-4")
scrapedName3 <- scrapedName3[1:45]

scrapedPrice3 <- scrapeNodes("span.a-offscreen")
scrapedPrice3 <- scrapedPrice3[1:45]

scrapedRatings3 <- scrapeNodes("span.a-icon-alt")
scrapedRatings3 <- scrapedRatings3[1:45]

scrapedReviews3 <- scrapeNodes("span.a-size-base.s-underline-text")
scrapedReviews3 <- scrapedReviews3[1:45]



pencil_products <- rbind(pencil_products, data.frame(category = scrapedCategory,name = scrapedName,
                    price = scrapedPrice,
                    ratings = scrapedRatings,
                    no_of_reviews = scrapedReviews))

pencil_products <- pencil_products[1:100,]


#View(pencil_products)
```
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
```{r}
library(dplyr)
library(rvest)
library(polite)
library(httr)
```
```{r}

sharpener_products <- data.frame()

sharpenerlink1 = "https://www.amazon.co.uk/s?k=sharpener&crid=GWWKI0LKL0N9&sprefix=sharpener%2Caps%2C481&ref=nb_sb_noss_1"

session4 <- bow(sharpenerlink1,
           user_agent = "For Educational Purpose")

scrapeNodes <- function(selector){
scrape(session) %>%
  html_nodes(selector) %>%
  html_text(trim = TRUE)
}

scrapedCategory4 <- "Sharpener"

scrapedsharpenerName <- scrapeNodes("h2.a-size-mini.a-spacing-none.a-color-base.s-line-clamp-4")
scrapedsharpenerName <- scrapedsharpenerName[1:45]

scrapedsharpenerPrice <- scrapeNodes("span.a-offscreen")
scrapedsharpenerPrice <- scrapedsharpenerPrice[1:45]

scrapedsharpenerRatings <- scrapeNodes("span.a-icon-alt")
scrapedsharpenerRatings <- scrapedsharpenerRatings[1:45]

scrapedsharpenerReviews <- scrapeNodes("span.a-size-base.s-underline-text")
scrapedsharpenerReviews <- scrapedsharpenerReviews[1:45]



sharpener_products <- rbind(sharpener_products, data.frame(category = scrapedCategory4,name = scrapedsharpenerName,
                    price = scrapedsharpenerPrice,
                    ratings = scrapedsharpenerRatings,
                    no_of_reviews = scrapedsharpenerReviews))
```
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
```{r}
sharpenerlink2 = "https://www.amazon.co.uk/s?k=sharpener&page=2&crid=GWWKI0LKL0N9&qid=1707586161&sprefix=sharpener%2Caps%2C481&ref=sr_pg_2"

session5 <- bow(sharpenerlink2,
           user_agent = "For Educational Purpose")

scrapeNodes <- function(selector){
scrape(session) %>%
  html_nodes(selector) %>%
  html_text(trim = TRUE)
}

scrapedCategory5 <- "Sharpener"

scrapedsharpenerName2 <- scrapeNodes("h2.a-size-mini.a-spacing-none.a-color-base.s-line-clamp-4")
scrapedsharpenerName2 <- scrapedsharpenerName2[1:45]

scrapedsharpenerPrice2 <- scrapeNodes("span.a-offscreen")
scrapedsharpenerPrice2 <- scrapedsharpenerPrice2[1:45]

scrapedsharpenerRatings2 <- scrapeNodes("span.a-icon-alt")
scrapedsharpenerRatings2 <- scrapedsharpenerRatings2[1:45]

scrapedsharpenerReviews2 <- scrapeNodes("span.a-size-base.s-underline-text")
scrapedsharpenerReviews2 <- scrapedsharpenerReviews2[1:45]



sharpener_products <- rbind(sharpener_products, data.frame(category = scrapedCategory5,name = scrapedsharpenerName2,
                    price = scrapedsharpenerPrice2,
                    ratings = scrapedsharpenerRatings2,
                    no_of_reviews = scrapedsharpenerReviews2))
```
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
```{r}
sharpenerlink3 = "https://www.amazon.co.uk/s?k=sharpener&page=3&crid=GWWKI0LKL0N9&qid=1707586828&sprefix=sharpener%2Caps%2C481&ref=sr_pg_3"

session6 <- bow(sharpenerlink3,
           user_agent = "For Educational Purpose")

scrapeNodes <- function(selector){
scrape(session) %>%
  html_nodes(selector) %>%
  html_text(trim = TRUE)
}

scrapedCategory6 <- "Sharpener"

scrapedsharpenerName3 <- scrapeNodes("h2.a-size-mini.a-spacing-none.a-color-base.s-line-clamp-4")
scrapedsharpenerName3 <- scrapedpencilName3[1:45]

scrapedsharpenerPrice3 <- scrapeNodes("span.a-offscreen")
scrapedsharpenerPrice3 <- scrapedsharpenerPrice3[1:45]

scrapedsharpenerRatings3 <- scrapeNodes("span.a-icon-alt")
scrapedsharpenerRatings3 <- scrapedsharpenerRatings3[1:45]

scrapedsharpenerReviews3 <- scrapeNodes("span.a-size-base.s-underline-text")
scrapedsharpenerReviews3 <- scrapedsharpenerReviews3[1:45]



sharpener_products <- rbind(sharpener_products, data.frame(category = scrapedCategory5,name = scrapedsharpenerName2,
                    price = scrapedsharpenerPrice2,
                    ratings = scrapedsharpenerRatings2,
                    no_of_reviews = scrapedsharpenerReviews2))

sharpener_products <- sharpener_products[1:100,]


#View(sharpener_products)
```
Merging Two Products
```{r}
scraped_products <- rbind(pencil_products, sharpener_products)
View(scraped_products)
```

10 PRODUCTS

product1
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product1 = data.frame()
scrapedCategory <- "Pencil"
~~~

  link = "https://www.amazon.co.uk/product-reviews/B09RB6YJLL/ref=cm_cr_arp_d_viewopt_sr?ie=UTF8&filterByStar=all_stars&reviewerType=all_reviews&pageNumber=1#reviews-filter-bar"
  
      sessionProd1 <- bow(link,
               user_agent = "For Educational Purpose")
  
      scrapeNodes <- function(selector){
      scrape(sessionProd1) %>%
        html_nodes(selector) %>%
        html_text(trim = TRUE)
      }
          
      scrapedprodName <- scrapeNodes("h1.a-size-large.a-text-ellipsis")
    
      
      scrapedReviewer <- scrapeNodes("span.a-profile-name")
      scrapedReviewer <- scrapedReviewer[1:10]

      
      scrapedReview <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      scrapedReview <- scrapedReview[1:10]

      
      scrapedDate <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      scrapedDate <- scrapedDate[1:10]

      
      scrapedprodRating <- scrapeNodes("span.a-icon-alt")
      scrapedprodRating <- scrapedprodRating[1:10]

      
      product1 <- rbind(product1, data.frame(category = scrapedCategory,name = scrapedprodName,
                          reviewer = scrapedReviewer,
                          review = scrapedReview,
                          date = scrapedDate,
                         ratings = scrapedprodRating))
```
~~~
```{r}
link2 = "https://www.amazon.co.uk/product-reviews/B09RB6YJLL/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&filterByStar=all_stars&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar"
  
  sessionProd2 <- bow(link2,
               user_agent = "For Educational Purpose")


      scrapedReviewer2 <- scrapeNodes("span.a-profile-name")
      scrapedReviewer2 <- scrapedReviewer2[1:10]

      
      scrapedReview2 <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      scrapedReview2 <- scrapedReview2[1:10]

      
      scrapedDate2 <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      scrapedDate2 <- scrapedDate2[1:10]

      
      scrapedprodRating2 <- scrapeNodes("span.a-icon-alt")
      scrapedprodRating2 <- scrapedprodRating2[1:10]

      
      product1 <- rbind(product1, data.frame(category = scrapedCategory ,name = scrapedprodName,
                          reviewer = scrapedReviewer2,
                          review = scrapedReview2,
                          date = scrapedDate2,
                         ratings = scrapedprodRating2))
```
~~~
```{r}
  link3 = "https://www.amazon.co.uk/product-reviews/B09RB6YJLL/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&filterByStar=all_stars&reviewerType=all_reviews&pageNumber=3#reviews-filter-bar"
  
  sessionProd3 <- bow(link3,
               user_agent = "For Educational Purpose")


      
      scrapedReviewer3 <- scrapeNodes("span.a-profile-name")
      scrapedReviewer3 <- scrapedReviewer3[1:10]

      
      scrapedReview3 <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      scrapedReview3 <- scrapedReview3[1:10]

      
      scrapedDate3 <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      scrapedDate3 <- scrapedDate3[1:10]

      
      scrapedprodRating3 <- scrapeNodes("span.a-icon-alt")
      scrapedprodRating3 <- scrapedprodRating3[1:10]

      
      product1 <- rbind(product1, data.frame(category = scrapedCategory ,name = scrapedprodName,
                          reviewer = scrapedReviewer3,
                          review = scrapedReview3,
                          date = scrapedDate3,
                         ratings = scrapedprodRating3))
      
View(product1)
```
product2
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product2 = data.frame()
scrapedCategory <- "Pencil"

~~~
 link = "https://www.amazon.co.uk/product-reviews/B009FYMXCU/ref=cm_cr_arp_d_viewopt_sr?ie=UTF8&filterByStar=all_stars&reviewerType=all_reviews&pageNumber=1#reviews-filter-bar"
  
      sessionProd1 <- bow(link,
               user_agent = "For Educational Purpose")
  
      scrapeNodes <- function(selector){
      scrape(sessionProd1) %>%
        html_nodes(selector) %>%
        html_text(trim = TRUE)
      }
          
      scrapedprodName <- scrapeNodes("h1.a-size-large.a-text-ellipsis")
    
      
      scrapedReviewer <- scrapeNodes("span.a-profile-name")
      scrapedReviewer <- scrapedReviewer[1:10]

      
      scrapedReview <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      scrapedReview <- scrapedReview[1:10]

      
      scrapedDate <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      scrapedDate <- scrapedDate[1:10]

      
      scrapedprodRating <- scrapeNodes("span.a-icon-alt")
      scrapedprodRating <- scrapedprodRating[1:10]

      
      product2 <- rbind(product2, data.frame(category = scrapedCategory,name = scrapedprodName,
                          reviewer = scrapedReviewer,
                          review = scrapedReview,
                          date = scrapedDate,
                         ratings = scrapedprodRating))
```
~~~
```{r}
link2 = "https://www.amazon.co.uk/product-reviews/B009FYMXCU/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&filterByStar=all_stars&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar"
  
  sessionProd2 <- bow(link2,
               user_agent = "For Educational Purpose")


      scrapedReviewer2 <- scrapeNodes("span.a-profile-name")
      scrapedReviewer2 <- scrapedReviewer2[1:10]

      
      scrapedReview2 <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      scrapedReview2 <- scrapedReview2[1:10]

      
      scrapedDate2 <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      scrapedDate2 <- scrapedDate2[1:10]

      
      scrapedprodRating2 <- scrapeNodes("span.a-icon-alt")
      scrapedprodRating2 <- scrapedprodRating2[1:10]

      
      product2 <- rbind(product2, data.frame(category = scrapedCategory ,name = scrapedprodName,
                          reviewer = scrapedReviewer2,
                          review = scrapedReview2,
                          date = scrapedDate2,
                         ratings = scrapedprodRating2))
```
~~~
```{r}
 link3 = "https://www.amazon.co.uk/product-reviews/B009FYMXCU/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&filterByStar=all_stars&reviewerType=all_reviews&pageNumber=3#reviews-filter-bar"
  
  sessionProd3 <- bow(link3,
               user_agent = "For Educational Purpose")


      
      scrapedReviewer3 <- scrapeNodes("span.a-profile-name")
      scrapedReviewer3 <- scrapedReviewer3[1:10]

      
      scrapedReview3 <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      scrapedReview3 <- scrapedReview3[1:10]

      
      scrapedDate3 <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      scrapedDate3 <- scrapedDate3[1:10]

      
      scrapedprodRating3 <- scrapeNodes("span.a-icon-alt")
      scrapedprodRating3 <- scrapedprodRating3[1:10]

      
      product2 <- rbind(product2, data.frame(category = scrapedCategory ,name = scrapedprodName,
                          reviewer = scrapedReviewer3,
                          review = scrapedReview3,
                          date = scrapedDate3,
                         ratings = scrapedprodRating3))
      
View(product2)
```

product3
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product3 = data.frame()
scrapedCategory <- "Pencil"

~~~
  
  link = "https://www.amazon.co.uk/product-reviews/B093L3F7GN/ref=cm_cr_arp_d_viewopt_sr?ie=UTF8&filterByStar=all_stars&reviewerType=all_reviews&pageNumber=1#reviews-filter-bar"
  
      sessionProd1 <- bow(link,
               user_agent = "For Educational Purpose")
  
      scrapeNodes <- function(selector){
      scrape(sessionProd1) %>%
        html_nodes(selector) %>%
        html_text(trim = TRUE)
      }
          
      scrapedprodName <- scrapeNodes("h1.a-size-large.a-text-ellipsis")
    
      
      scrapedReviewer <- scrapeNodes("span.a-profile-name")
      scrapedReviewer <- scrapedReviewer[1:10]

      
      scrapedReview <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      scrapedReview <- scrapedReview[1:10]

      
      scrapedDate <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      scrapedDate <- scrapedDate[1:10]

      
      scrapedprodRating <- scrapeNodes("span.a-icon-alt")
      scrapedprodRating <- scrapedprodRating[1:10]

      
      product3 <- rbind(product3, data.frame(category = scrapedCategory,name = scrapedprodName,
                          reviewer = scrapedReviewer,
                          review = scrapedReview,
                          date = scrapedDate,
                         ratings = scrapedprodRating))
~~~

      link2 = "https://www.amazon.co.uk/product-reviews/B093L3F7GN/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&filterByStar=all_stars&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar"
  
  sessionProd2 <- bow(link2,
               user_agent = "For Educational Purpose")


      scrapedReviewer2 <- scrapeNodes("span.a-profile-name")
      scrapedReviewer2 <- scrapedReviewer2[1:10]

      
      scrapedReview2 <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      scrapedReview2 <- scrapedReview2[1:10]

      
      scrapedDate2 <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      scrapedDate2 <- scrapedDate2[1:10]

      
      scrapedprodRating2 <- scrapeNodes("span.a-icon-alt")
      scrapedprodRating2 <- scrapedprodRating2[1:10]

      
      product3 <- rbind(product3, data.frame(category = scrapedCategory ,name = scrapedprodName,
                          reviewer = scrapedReviewer2,
                          review = scrapedReview2,
                          date = scrapedDate2,
                         ratings = scrapedprodRating2))
      
      
~~~
      
      link3 = "https://www.amazon.co.uk/product-reviews/B093L3F7GN/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&filterByStar=all_stars&reviewerType=all_reviews&pageNumber=3#reviews-filter-bar"
  
  sessionProd3 <- bow(link3,
               user_agent = "For Educational Purpose")


      
      scrapedReviewer3 <- scrapeNodes("span.a-profile-name")
      scrapedReviewer3 <- scrapedReviewer3[1:10]

      
      scrapedReview3 <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      scrapedReview3 <- scrapedReview3[1:10]

      
      scrapedDate3 <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      scrapedDate3 <- scrapedDate3[1:10]

      
      scrapedprodRating3 <- scrapeNodes("span.a-icon-alt")
      scrapedprodRating3 <- scrapedprodRating3[1:10]

      
      product3 <- rbind(product3, data.frame(category = scrapedCategory ,name = scrapedprodName,
                          reviewer = scrapedReviewer3,
                          review = scrapedReview3,
                          date = scrapedDate3,
                         ratings = scrapedprodRating3))
      
View(product3)
```
product4
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product4 = data.frame()
scrapedCategory <- "Pencil"


~~~

  link = "https://www.amazon.co.uk/product-reviews/B071JM699B/ref=cm_cr_arp_d_viewopt_sr?ie=UTF8&filterByStar=all_stars&reviewerType=all_reviews&pageNumber=1#reviews-filter-bar"
  
      sessionProd1 <- bow(link,
               user_agent = "For Educational Purpose")
  
      scrapeNodes <- function(selector){
      scrape(sessionProd1) %>%
        html_nodes(selector) %>%
        html_text(trim = TRUE)
      }
          
      scrapedprodName <- scrapeNodes("h1.a-size-large.a-text-ellipsis")
    
      
      scrapedReviewer <- scrapeNodes("span.a-profile-name")
      scrapedReviewer <- scrapedReviewer[1:10]

      
      scrapedReview <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      scrapedReview <- scrapedReview[1:10]

      
      scrapedDate <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      scrapedDate <- scrapedDate[1:10]

      
      scrapedprodRating <- scrapeNodes("span.a-icon-alt")
      scrapedprodRating <- scrapedprodRating[1:10]

      
      product4 <- rbind(product4, data.frame(category = scrapedCategory,name = scrapedprodName,
                          reviewer = scrapedReviewer,
                          review = scrapedReview,
                          date = scrapedDate,
                         ratings = scrapedprodRating))
~~~

      link2 = "https://www.amazon.co.uk/product-reviews/B071JM699B/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&filterByStar=all_stars&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar"
  
  sessionProd2 <- bow(link2,
               user_agent = "For Educational Purpose")


      scrapedReviewer2 <- scrapeNodes("span.a-profile-name")
      scrapedReviewer2 <- scrapedReviewer2[1:10]

      
      scrapedReview2 <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      scrapedReview2 <- scrapedReview2[1:10]

      
      scrapedDate2 <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      scrapedDate2 <- scrapedDate2[1:10]

      
      scrapedprodRating2 <- scrapeNodes("span.a-icon-alt")
      scrapedprodRating2 <- scrapedprodRating2[1:10]

      
      product4 <- rbind(product4, data.frame(category = scrapedCategory ,name = scrapedprodName,
                          reviewer = scrapedReviewer2,
                          review = scrapedReview2,
                          date = scrapedDate2,
                         ratings = scrapedprodRating2))
      
      
~~~
      
      link3 = "https://www.amazon.co.uk/product-reviews/B071JM699B/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&filterByStar=all_stars&reviewerType=all_reviews&pageNumber=3#reviews-filter-bar"
  
  sessionProd3 <- bow(link3,
               user_agent = "For Educational Purpose")


      
      scrapedReviewer3 <- scrapeNodes("span.a-profile-name")
      scrapedReviewer3 <- scrapedReviewer3[1:10]

      
      scrapedReview3 <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      scrapedReview3 <- scrapedReview3[1:10]

      
      scrapedDate3 <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      scrapedDate3 <- scrapedDate3[1:10]

      
      scrapedprodRating3 <- scrapeNodes("span.a-icon-alt")
      scrapedprodRating3 <- scrapedprodRating3[1:10]

      
      product4 <- rbind(product4, data.frame(category = scrapedCategory ,name = scrapedprodName,
                          reviewer = scrapedReviewer3,
                          review = scrapedReview3,
                          date = scrapedDate3,
                         ratings = scrapedprodRating3))
      
View(product4)
```
product5
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product5 = data.frame()
scrapedCategory <- "Pencil"


###

  link = "https://www.amazon.co.uk/product-reviews/B003V8BIFE/ref=cm_cr_arp_d_viewopt_sr?ie=UTF8&filterByStar=all_stars&reviewerType=all_reviews&pageNumber=1#reviews-filter-bar"
  
      sessionProd1 <- bow(link,
               user_agent = "For Educational Purpose")
  
      scrapeNodes <- function(selector){
      scrape(sessionProd1) %>%
        html_nodes(selector) %>%
        html_text(trim = TRUE)
      }
          
      scrapedprodName <- scrapeNodes("h1.a-size-large.a-text-ellipsis")
    
      
      scrapedReviewer <- scrapeNodes("span.a-profile-name")
      scrapedReviewer <- scrapedReviewer[1:10]

      
      scrapedReview <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      scrapedReview <- scrapedReview[1:10]

      
      scrapedDate <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      scrapedDate <- scrapedDate[1:10]

      
      scrapedprodRating <- scrapeNodes("span.a-icon-alt")
      scrapedprodRating <- scrapedprodRating[1:10]

      
      product5 <- rbind(product5, data.frame(category = scrapedCategory,name = scrapedprodName,
                          reviewer = scrapedReviewer,
                          review = scrapedReview,
                          date = scrapedDate,
                         ratings = scrapedprodRating))
~~~

      link2 = "https://www.amazon.co.uk/product-reviews/B003V8BIFE/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&filterByStar=all_stars&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar"
  
  sessionProd2 <- bow(link2,
               user_agent = "For Educational Purpose")


      scrapedReviewer2 <- scrapeNodes("span.a-profile-name")
      scrapedReviewer2 <- scrapedReviewer2[1:10]

      
      scrapedReview2 <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      scrapedReview2 <- scrapedReview2[1:10]

      
      scrapedDate2 <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      scrapedDate2 <- scrapedDate2[1:10]

      
      scrapedprodRating2 <- scrapeNodes("span.a-icon-alt")
      scrapedprodRating2 <- scrapedprodRating2[1:10]

      
      product5 <- rbind(product5, data.frame(category = scrapedCategory ,name = scrapedprodName,
                          reviewer = scrapedReviewer2,
                          review = scrapedReview2,
                          date = scrapedDate2,
                         ratings = scrapedprodRating2))
      
      
 ~~~
      
      link3 = "https://www.amazon.co.uk/product-reviews/B003V8BIFE/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&filterByStar=all_stars&reviewerType=all_reviews&pageNumber=3#reviews-filter-bar"
  
  sessionProd3 <- bow(link3,
               user_agent = "For Educational Purpose")


      
      scrapedReviewer3 <- scrapeNodes("span.a-profile-name")
      scrapedReviewer3 <- scrapedReviewer3[1:10]

      
      scrapedReview3 <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      scrapedReview3 <- scrapedReview3[1:10]

      
      scrapedDate3 <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      scrapedDate3 <- scrapedDate3[1:10]

      
      scrapedprodRating3 <- scrapeNodes("span.a-icon-alt")
      scrapedprodRating3 <- scrapedprodRating3[1:10]

      
      product5 <- rbind(product5, data.frame(category = scrapedCategory ,name = scrapedprodName,
                          reviewer = scrapedReviewer3,
                          review = scrapedReview3,
                          date = scrapedDate3,
                         ratings = scrapedprodRating3))
      
View(product5)
```
product6
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product6 = data.frame()
scrapedCategory <- "Sharpener"


~~~

  link = "https://www.amazon.co.uk/product-reviews/B00XJDMM2O/ref=cm_cr_arp_d_viewopt_sr?ie=UTF8&filterByStar=all_stars&reviewerType=all_reviews&pageNumber=1#reviews-filter-bar"
  
      sessionProd1 <- bow(link,
               user_agent = "For Educational Purpose")
  
      scrapeNodes <- function(selector){
      scrape(sessionProd1) %>%
        html_nodes(selector) %>%
        html_text(trim = TRUE)
      }
          
      scrapedprodName <- scrapeNodes("h1.a-size-large.a-text-ellipsis")
    
      
      scrapedReviewer <- scrapeNodes("span.a-profile-name")
      scrapedReviewer <- scrapedReviewer[1:10]

      
      scrapedReview <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      scrapedReview <- scrapedReview[1:10]

      
      scrapedDate <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      scrapedDate <- scrapedDate[1:10]

      
      scrapedprodRating <- scrapeNodes("span.a-icon-alt")
      scrapedprodRating <- scrapedprodRating[1:10]

      
      product6 <- rbind(product6, data.frame(category = scrapedCategory,name = scrapedprodName,
                          reviewer = scrapedReviewer,
                          review = scrapedReview,
                          date = scrapedDate,
                         ratings = scrapedprodRating))
~~~

      link2 = "https://www.amazon.co.uk/product-reviews/B00XJDMM2O/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&filterByStar=all_stars&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar"
  
  sessionProd2 <- bow(link2,
               user_agent = "For Educational Purpose")


      scrapedReviewer2 <- scrapeNodes("span.a-profile-name")
      scrapedReviewer2 <- scrapedReviewer2[1:10]

      
      scrapedReview2 <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      scrapedReview2 <- scrapedReview2[1:10]

      
      scrapedDate2 <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      scrapedDate2 <- scrapedDate2[1:10]

      
      scrapedprodRating2 <- scrapeNodes("span.a-icon-alt")
      scrapedprodRating2 <- scrapedprodRating2[1:10]

      
      product6 <- rbind(product6, data.frame(category = scrapedCategory ,name = scrapedprodName,
                          reviewer = scrapedReviewer2,
                          review = scrapedReview2,
                          date = scrapedDate2,
                         ratings = scrapedprodRating2))
      
      
~~~
      
      link3 = "https://www.amazon.co.uk/product-reviews/B00XJDMM2O/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&filterByStar=all_stars&reviewerType=all_reviews&pageNumber=3#reviews-filter-bar"
  
  sessionProd3 <- bow(link3,
               user_agent = "For Educational Purpose")


      
      scrapedReviewer3 <- scrapeNodes("span.a-profile-name")
      scrapedReviewer3 <- scrapedReviewer3[1:10]

      
      scrapedReview3 <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      scrapedReview3 <- scrapedReview3[1:10]

      
      scrapedDate3 <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      scrapedDate3 <- scrapedDate3[1:10]

      
      scrapedprodRating3 <- scrapeNodes("span.a-icon-alt")
      scrapedprodRating3 <- scrapedprodRating3[1:10]

      
      product6 <- rbind(product6, data.frame(category = scrapedCategory ,name = scrapedprodName,
                          reviewer = scrapedReviewer3,
                          review = scrapedReview3,
                          date = scrapedDate3,
                         ratings = scrapedprodRating3))
      
View(product6)
```
product7
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product7 = data.frame()
scrapedCategory <- "Sharpener"


~~~

  link = "https://www.amazon.co.uk/product-reviews/B000KJMM5C/ref=cm_cr_arp_d_viewopt_sr?ie=UTF8&filterByStar=all_stars&reviewerType=all_reviews&pageNumber=1#reviews-filter-bar"
  
      sessionProd1 <- bow(link,
               user_agent = "For Educational Purpose")
  
      scrapeNodes <- function(selector){
      scrape(sessionProd1) %>%
        html_nodes(selector) %>%
        html_text(trim = TRUE)
      }
          
      scrapedprodName <- scrapeNodes("h1.a-size-large.a-text-ellipsis")
    
      
      scrapedReviewer <- scrapeNodes("span.a-profile-name")
      scrapedReviewer <- scrapedReviewer[1:10]

      
      scrapedReview <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      scrapedReview <- scrapedReview[1:10]

      
      scrapedDate <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      scrapedDate <- scrapedDate[1:10]

      
      scrapedprodRating <- scrapeNodes("span.a-icon-alt")
      scrapedprodRating <- scrapedprodRating[1:10]

      
      product7 <- rbind(product7, data.frame(category = scrapedCategory,name = scrapedprodName,
                          reviewer = scrapedReviewer,
                          review = scrapedReview,
                          date = scrapedDate,
                         ratings = scrapedprodRating))
~~~

      link2 = "https://www.amazon.co.uk/product-reviews/B000KJMM5C/ref=cm_cr_getr_d_paging_btm_next_2?ie=UTF8&filterByStar=all_stars&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar"
  
  sessionProd2 <- bow(link2,
               user_agent = "For Educational Purpose")


      scrapedReviewer2 <- scrapeNodes("span.a-profile-name")
      scrapedReviewer2 <- scrapedReviewer2[1:10]

      
      scrapedReview2 <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      scrapedReview2 <- scrapedReview2[1:10]

      
      scrapedDate2 <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      scrapedDate2 <- scrapedDate2[1:10]

      
      scrapedprodRating2 <- scrapeNodes("span.a-icon-alt")
      scrapedprodRating2 <- scrapedprodRating2[1:10]

      
      product7 <- rbind(product7, data.frame(category = scrapedCategory ,name = scrapedprodName,
                          reviewer = scrapedReviewer2,
                          review = scrapedReview2,
                          date = scrapedDate2,
                         ratings = scrapedprodRating2))
      
      
~~~
      
      link3 = "https://www.amazon.co.uk/product-reviews/B000KJMM5C/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&filterByStar=all_stars&reviewerType=all_reviews&pageNumber=3#reviews-filter-bar"
  
  sessionProd3 <- bow(link3,
               user_agent = "For Educational Purpose")


      
      scrapedReviewer3 <- scrapeNodes("span.a-profile-name")
      scrapedReviewer3 <- scrapedReviewer3[1:10]

      
      scrapedReview3 <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      scrapedReview3 <- scrapedReview3[1:10]

      
      scrapedDate3 <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      scrapedDate3 <- scrapedDate3[1:10]

      
      scrapedprodRating3 <- scrapeNodes("span.a-icon-alt")
      scrapedprodRating3 <- scrapedprodRating3[1:10]

      
      product7 <- rbind(product7, data.frame(category = scrapedCategory ,name = scrapedprodName,
                          reviewer = scrapedReviewer3,
                          review = scrapedReview3,
                          date = scrapedDate3,
                         ratings = scrapedprodRating3))
      
View(product7)
```
product8
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product8 = data.frame()
scrapedCategory <- "Sharpener"

~~~

  link = "https://www.amazon.co.uk/product-reviews/B00ENI2G48/ref=cm_cr_arp_d_viewopt_sr?ie=UTF8&filterByStar=all_stars&reviewerType=all_reviews&pageNumber=1#reviews-filter-bar"
  
      sessionProd1 <- bow(link,
               user_agent = "For Educational Purpose")
  
      scrapeNodes <- function(selector){
      scrape(sessionProd1) %>%
        html_nodes(selector) %>%
        html_text(trim = TRUE)
      }
          
      scrapedprodName <- scrapeNodes("h1.a-size-large.a-text-ellipsis")
    
      
      scrapedReviewer <- scrapeNodes("span.a-profile-name")
      scrapedReviewer <- scrapedReviewer[1:10]

      
      scrapedReview <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      scrapedReview <- scrapedReview[1:10]

      
      scrapedDate <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      scrapedDate <- scrapedDate[1:10]

      
      scrapedprodRating <- scrapeNodes("span.a-icon-alt")
      scrapedprodRating <- scrapedprodRating[1:10]

      
      product8 <- rbind(product8, data.frame(category = scrapedCategory,name = scrapedprodName,
                          reviewer = scrapedReviewer,
                          review = scrapedReview,
                          date = scrapedDate,
                         ratings = scrapedprodRating))
~~~

      link2 = "https://www.amazon.co.uk/product-reviews/B00ENI2G48/ref=cm_cr_getr_d_paging_btm_next_2?ie=UTF8&filterByStar=all_stars&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar"
  
  sessionProd2 <- bow(link2,
               user_agent = "For Educational Purpose")


      scrapedReviewer2 <- scrapeNodes("span.a-profile-name")
      scrapedReviewer2 <- scrapedReviewer2[1:10]

      
      scrapedReview2 <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      scrapedReview2 <- scrapedReview2[1:10]

      
      scrapedDate2 <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      scrapedDate2 <- scrapedDate2[1:10]

      
      scrapedprodRating2 <- scrapeNodes("span.a-icon-alt")
      scrapedprodRating2 <- scrapedprodRating2[1:10]

      
      product8 <- rbind(product8, data.frame(category = scrapedCategory ,name = scrapedprodName,
                          reviewer = scrapedReviewer2,
                          review = scrapedReview2,
                          date = scrapedDate2,
                         ratings = scrapedprodRating2))
      
      
~~~
      
      link3 = "https://www.amazon.co.uk/product-reviews/B00ENI2G48/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&filterByStar=all_stars&reviewerType=all_reviews&pageNumber=3#reviews-filter-bar"
  
  sessionProd3 <- bow(link3,
               user_agent = "For Educational Purpose")


      
      scrapedReviewer3 <- scrapeNodes("span.a-profile-name")
      scrapedReviewer3 <- scrapedReviewer3[1:10]

      
      scrapedReview3 <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      scrapedReview3 <- scrapedReview3[1:10]

      
      scrapedDate3 <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      scrapedDate3 <- scrapedDate3[1:10]

      
      scrapedprodRating3 <- scrapeNodes("span.a-icon-alt")
      scrapedprodRating3 <- scrapedprodRating3[1:10]

      
      product8 <- rbind(product8, data.frame(category = scrapedCategory ,name = scrapedprodName,
                          reviewer = scrapedReviewer3,
                          review = scrapedReview3,
                          date = scrapedDate3,
                         ratings = scrapedprodRating3))
      
View(product8)
```
product9
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product9 = data.frame()
scrapedCategory <- "Sharpener"


~~~

  link = "https://www.amazon.co.uk/product-reviews/B0009WFNY2/ref=cm_cr_arp_d_viewopt_sr?ie=UTF8&filterByStar=all_stars&reviewerType=all_reviews&pageNumber=1#reviews-filter-bar"
  
      sessionProd1 <- bow(link,
               user_agent = "For Educational Purpose")
  
      scrapeNodes <- function(selector){
      scrape(sessionProd1) %>%
        html_nodes(selector) %>%
        html_text(trim = TRUE)
      }
          
      scrapedprodName <- scrapeNodes("h1.a-size-large.a-text-ellipsis")
    
      
      scrapedReviewer <- scrapeNodes("span.a-profile-name")
      scrapedReviewer <- scrapedReviewer[1:10]

      
      scrapedReview <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      scrapedReview <- scrapedReview[1:10]

      
      scrapedDate <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      scrapedDate <- scrapedDate[1:10]

      
      scrapedprodRating <- scrapeNodes("span.a-icon-alt")
      scrapedprodRating <- scrapedprodRating[1:10]

      
      product9 <- rbind(product9, data.frame(category = scrapedCategory,name = scrapedprodName,
                          reviewer = scrapedReviewer,
                          review = scrapedReview,
                          date = scrapedDate,
                         ratings = scrapedprodRating))
~~~

      link2 = "https://www.amazon.co.uk/product-reviews/B0009WFNY2/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&filterByStar=all_stars&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar"
  
  sessionProd2 <- bow(link2,
               user_agent = "For Educational Purpose")


      scrapedReviewer2 <- scrapeNodes("span.a-profile-name")
      scrapedReviewer2 <- scrapedReviewer2[1:10]

      
      scrapedReview2 <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      scrapedReview2 <- scrapedReview2[1:10]

      
      scrapedDate2 <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      scrapedDate2 <- scrapedDate2[1:10]

      
      scrapedprodRating2 <- scrapeNodes("span.a-icon-alt")
      scrapedprodRating2 <- scrapedprodRating2[1:10]

      
      product9 <- rbind(product9, data.frame(category = scrapedCategory ,name = scrapedprodName,
                          reviewer = scrapedReviewer2,
                          review = scrapedReview2,
                          date = scrapedDate2,
                         ratings = scrapedprodRating2))
      
      
~~~
      
      link3 = "https://www.amazon.co.uk/product-reviews/B0009WFNY2/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&filterByStar=all_stars&reviewerType=all_reviews&pageNumber=3#reviews-filter-bar"
  
  sessionProd3 <- bow(link3,
               user_agent = "For Educational Purpose")


      
      scrapedReviewer3 <- scrapeNodes("span.a-profile-name")
      scrapedReviewer3 <- scrapedReviewer3[1:10]

      
      scrapedReview3 <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      scrapedReview3 <- scrapedReview3[1:10]

      
      scrapedDate3 <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      scrapedDate3 <- scrapedDate3[1:10]

      
      scrapedprodRating3 <- scrapeNodes("span.a-icon-alt")
      scrapedprodRating3 <- scrapedprodRating3[1:10]

      
      product9 <- rbind(product9, data.frame(category = scrapedCategory ,name = scrapedprodName,
                          reviewer = scrapedReviewer3,
                          review = scrapedReview3,
                          date = scrapedDate3,
                         ratings = scrapedprodRating3))
      
View(product9)
```
product10
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product10 = data.frame()
scrapedCategory <- "Sharpener"


~~~

  link = "https://www.amazon.co.uk/product-reviews/B00OPQZ2A8/ref=cm_cr_arp_d_viewopt_sr?ie=UTF8&filterByStar=all_stars&reviewerType=all_reviews&pageNumber=1#reviews-filter-bar"
  
      sessionProd1 <- bow(link,
               user_agent = "For Educational Purpose")
  
      scrapeNodes <- function(selector){
      scrape(sessionProd1) %>%
        html_nodes(selector) %>%
        html_text(trim = TRUE)
      }
          
      scrapedprodName <- scrapeNodes("h1.a-size-large.a-text-ellipsis")
    
      
      scrapedReviewer <- scrapeNodes("span.a-profile-name")
      scrapedReviewer <- scrapedReviewer[1:10]

      
      scrapedReview <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      scrapedReview <- scrapedReview[1:10]

      
      scrapedDate <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      scrapedDate <- scrapedDate[1:10]

      
      scrapedprodRating <- scrapeNodes("span.a-icon-alt")
      scrapedprodRating <- scrapedprodRating[1:10]

      
      product10 <- rbind(product10, data.frame(category = scrapedCategory,name = scrapedprodName,
                          reviewer = scrapedReviewer,
                          review = scrapedReview,
                          date = scrapedDate,
                         ratings = scrapedprodRating))
~~~

      link2 = "https://www.amazon.co.uk/product-reviews/B00OPQZ2A8/ref=cm_cr_getr_d_paging_btm_next_2?ie=UTF8&filterByStar=all_stars&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar"
  
  sessionProd2 <- bow(link2,
               user_agent = "For Educational Purpose")


      scrapedReviewer2 <- scrapeNodes("span.a-profile-name")
      scrapedReviewer2 <- scrapedReviewer2[1:10]

      
      scrapedReview2 <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      scrapedReview2 <- scrapedReview2[1:10]

      
      scrapedDate2 <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      scrapedDate2 <- scrapedDate2[1:10]

      
      scrapedprodRating2 <- scrapeNodes("span.a-icon-alt")
      scrapedprodRating2 <- scrapedprodRating2[1:10]

      
      product10 <- rbind(product10, data.frame(category = scrapedCategory ,name = scrapedprodName,
                          reviewer = scrapedReviewer2,
                          review = scrapedReview2,
                          date = scrapedDate2,
                         ratings = scrapedprodRating2))
      
      
~~~
      
      link3 = "https://www.amazon.co.uk/product-reviews/B00OPQZ2A8/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&filterByStar=all_stars&reviewerType=all_reviews&pageNumber=3#reviews-filter-bar"
  
  sessionProd3 <- bow(link3,
               user_agent = "For Educational Purpose")


      
      scrapedReviewer3 <- scrapeNodes("span.a-profile-name")
      scrapedReviewer3 <- scrapedReviewer3[1:10]

      
      scrapedReview3 <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      scrapedReview3 <- scrapedReview3[1:10]

      
      scrapedDate3 <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      scrapedDate3 <- scrapedDate3[1:10]

      
      scrapedprodRating3 <- scrapeNodes("span.a-icon-alt")
      scrapedprodRating3 <- scrapedprodRating3[1:10]

      
      product10 <- rbind(product10, data.frame(category = scrapedCategory ,name = scrapedprodName,
                          reviewer = scrapedReviewer3,
                          review = scrapedReview3,
                          date = scrapedDate3,
                         ratings = scrapedprodRating3))
      
View(product10)
```

```{r}

all_reviews <- rbind(product1, product2, product3, product4, product5, product6, product7, product8, product9, product10)
View(all_reviews)


#install.packages("usethis")
library(usethis)
```

